---
editor_options: 
  markdown: 
    wrap: 80
---

# Purpose

This is a helper script that loads all necessary packages to run the targets
pipeline, then runs it to acquire Landsat Collection 2 surface reflectance and
surface temperature for user-defined areas of interest (AOI). While this script
is written in an .Rmd script, we recommend walking through this script manually,
as the knit function often runs into issues and this script has a number of
interactive steps.

## Pre-requisites

siteSR_WQP relies on a configuration file (`config.yml`) to run specific
profiles that determine what operations are being run. The file contains three
configuration profiles: "default", "admin_update", and "use_stable".

-   "default" runs the pipeline without using any publicaly-stable versions of
    datasets made with AquaMatch_harmonize_WQP. This requires that the
    AquaMatch_harmonize_WQP pipeline has been run locally.

-   "use_stable" uses publicly-posted stable versions of datasets from
    AquaMatch_harmonize_WQP and is intended for those who wish to modify choices
    made in siteSR_WQP or for those who wish to have the complete pipeline on
    their local device. This is the recommended setting for most users.

-   "admin_update" is intended for use by ROSSyndicate members when updating
    siteSR datasets and create publicly-stable versions of the siteSR_WQP to be
    stored in the AquaMatch_siteSR_WQP repository.

All configurations will be reliant on the stable version of handoff coefficients
calculated in AquaMatch_lakeSR.

Proper configuration of harmonize_repo_directory and lakeSR_repo_directory is
imperative as the siteSR_WQP workflow references files inside
AquaMatch_harmonize_WQP and AquaMatch_lakeSR file structures. If this is
incorrectly set up, users will receive a message to communicate this and the
workflow will stop. All repositories stored on the AquaSat v2 GitHub will
contain files that link to versions of the data that the AquaSat v2 team has
harmonized so that a local run is not necessitated. Any run of the "default"
configuration will require that the harmonize pipeline has been run locally.

## Install necessary packages

```{r package_installer, echo = F}
package_installer <- function(x) {
  if (x %in% installed.packages()) {
    print(paste0('{', x ,'} package is already installed.'))
    } else {
      install.packages(x)
      print(paste0('{', x ,'} package has been installed.'))
    }
  }
```

List packages that need to be checked for install, and walk the function along
them all.

```{r walk_package_installer, message = F}
packages <- c('tidyverse',
              'reticulate',
              'targets',
              'tarchetypes',
              'yaml',
              'nhdplusTools',
              'polylabelr',
              'sf')

lapply(packages, package_installer)
```

## Authenticate and initialize Earth Engine

You will need to have [installed and initialized the
`gcloud CLI`](https://cloud.google.com/sdk/docs/install) and have a [Google
Earth Engine account](https://code.earthengine.google.com/register) prior to
running this workflow. Some common troubleshooting solutions [can be found
here]<https://github.com/rossyndicate/ROSS_RS_mini_tools/blob/main/helps/CommonIssues.md>).

### Authentication

To authenticate your GEE account, we will use a Python environment created in
the R file 'src/py/pySetup.R'. This will take a few minutes if you haven't yet
run the python setup script while it creates a virtual environment.

```{r}
source('src/py/pySetup.R')
```

### Authenticate your instance of GEE

```{python}
import ee

ee.Authenticate(auth_mode = 'localhost')
```

### Configuration

We use a configuration file (`gee_config.yml`) for the GEE run, as well as a
general configuration file (`config.yml`). If you are outside of the ROSS team,
you will need to update some entries in the configuration file and update the
settings for the `p0_siteSR_config` target in the `_targets.R` script in order
to successfully run this workflow.

## Run the targets pipeline and output a network graph.

```{r run_targets, echo = F}
library(targets)

tar_make(p99_make_target_ids)

tar_visnetwork()
```
