
# Purpose

This is a helper script that loads all necessary packages to run the targets 
pipeline, then runs it to acquire Landsat Collection 2 surface reflectance and
surface temperature for user-defined areas of interest (AOI). While this script
is written in an .Rmd script, we recommend walking through this script manually, 
as the knit function often runs into issues and this script has a number of 
interactive steps.

## Install necessary packages

```{r package_installer, echo = F}
package_installer <- function(x) {
  if (x %in% installed.packages()) {
    print(paste0('{', x ,'} package is already installed.'))
    } else {
      install.packages(x)
      print(paste0('{', x ,'} package has been installed.'))
    }
  }
```

List packages that need to be checked for install, and walk the function along them all.

```{r walk_package_installer, message = F}
packages <- c('tidyverse',
              'reticulate',
              'targets',
              'tarchetypes',
              'yaml',
              'nhdplusTools',
              'polylabelr',
              'sf')

lapply(packages, package_installer)
```

<!-- ## Authenticate and initialize Earth Engine -->

<!-- You will need to have [installed and initialized the `gcloud CLI`](https://cloud.google.com/sdk/docs/install)  -->
<!-- and have a [Google Earth Engine account](https://code.earthengine.google.com/register)  -->
<!-- prior to running this workflow. Some common troubleshooting solutions  -->
<!-- [can be found here]<https://github.com/rossyndicate/ROSS_RS_mini_tools/blob/main/helps/CommonIssues.md>). -->

<!-- ### Authentication -->

<!-- To authenticate your GEE account, we will use a Python environment created in the  -->
<!-- R file 'data_acquisition/src/py/pySetup.R'. This will take a few minutes if you  -->
<!-- haven't yet run the python setup script while it creates a virtual environment. -->

<!-- ```{r} -->
<!-- source('src/py/pySetup.R') -->
<!-- ``` -->

<!-- ### Authenticate your instance of GEE -->

<!-- ```{python} -->
<!-- import ee -->

<!-- ee.Authenticate(auth_mode = 'localhost') -->
<!-- ``` -->

## Run the targets pipeline and output a network graph.

```{r run_targets, echo = F}
library(targets)

tar_make(p4_WQP_site_NHD_info)

tar_visnetwork()
```


